Unveiling the 2022 Iran Protests: Insights from HRANA's Dataset

### 2024-04-17 paper/paper.qmd
Revised all before result section

kable(selected_columns, 
      format = "markdown", 
      align = "c",
      caption = "Ten Random Dataset Compiled By HRANA",
      label = "tbl-protest-data")|>
  kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)

@@

@fig-arrests-detainees illustrates the cumulative count of arrests and detainees identified over time during the protests. The area chart displays the progression of these two metrics, providing insights into the trend of arrests and detentions throughout the specified period. The light gray area represents the cumulative count of individuals arrested, while the dark gray area represents the cumulative count of detainees identified.

@@

ggplot(protest_data, aes(x = as.Date(Date, format="%m/%d/%Y"))) +
  geom_area(aes(y = Arrested, fill = "Individuals Arrested")) +
  geom_area(aes(y = Detainees, fill = "Detainees Identified")) +
  theme_minimal() +
  labs(x = "Date", y = "Cumulative Count", fill = "Fill") +
  scale_fill_manual(values = c("Individuals Arrested" = "lightgray", "Detainees Identified" = "darkgray"))

@@

The analysis provides compelling insights into the arrest dynamics during the 158 days. The @fig-total-arrested depicts the total number of individuals arrested compared to the subset of students among them.

The @fig-total-arrested illustrates the stark difference between the total number of individuals arrested and the number of students among them. The dark gray bars represent the total number of arrested individuals, while the light gray bars specifically denote the total number of students arrested. This visualization effectively highlights the proportion of students within the broader context of arrests during the protests.

>>>>

kable(selected_columns, 
      format = "markdown", 
      align = "c",
      caption = "Ten Random Entries Compiled By HRANA",
      label = "tbl-protest-data")|>
  kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)

@@

@fig-arrests-detainees illustrates the cumulative count of arrests and detainees identified over time during the protests.Detainees are people who were held in custody temporarily for less than 24 hours, while arrests consist of individuals who may still be in prison. By tracking both metrics, we can gain valuable insights into the authorities' response to the protests and the way they treat individuals involved. The area chart displays the progression of these two metrics, providing insights into the trend of arrests and detentions throughout the specified period. The light gray area represents the cumulative count of individuals arrested, while the dark gray area represents the cumulative count of detainees identified.

@@

ggplot(protest_data, aes(x = as.Date(Date, format="%m/%d/%Y"))) +
  geom_area(aes(y = Arrested, fill = "Individuals Arrested")) +
  geom_area(aes(y = Detainees, fill = "Detainees Identified")) +
  theme_minimal() +
  labs(x = "Date", y = "Cumulative Count of Arrests and Detainees", fill = "Legend") +
  scale_fill_manual(values = c("Individuals Arrested" = "lightgray", "Detainees Identified" = "darkgray"))

@@

The analysis provides compelling insights into the arrest dynamics during the 158 days. @fig-total-arrested depicts the total number of individuals arrested compared to the subset of students among them.

@fig-total-arrested illustrates the stark difference between the total number of individuals arrested and the number of students among them. The dark gray bars represent the total number of arrested individuals, while the light gray bars specifically denote the total number of students arrested. This visualization effectively highlights the proportion of students within the broader context of arrests during the protests.
